Implications of afforestation policies for global markets

### 2023-05-31 paper.Rmd
Update paper.Rmd

# Introduction
In 2023, there are 4.1 billion hectares of forestland globally,which covered roughly 31.4% of the land [@fao2023]. These forests play an important role in maintaining and growing the land-based carbon sink, currently sequestering about 30% of GHG emmissions [@roe2019]. With increasingly negative climate impacts, the pressure to enhance the terrestrial sink is growing, and one of the tools to achieve this is through afforestation. In fact, many of the Nationally Determined Contributions (NDCs) countries have submitted that detail their plans to keep warming under the 2C threshold rely to a significant degree on afforestation projects [@roe2019]. This is because of forests proven ability to sequester carbon not only the stems of trees [@davis2022] but their soils as well [@guo2021].  At the same time, forests are continually threatened by issues such as rising incomes and food prices and population growth that put pressure on policymakers to allow greater conversion of forestland into farmland. Previous research though has suggested that substantive gains in the carbon sink (+23.8PgCo2e/yr) can be made without sacrificing agricultural land [@griscom2017]. Thus, the manner in which these various and oftentimes competing concerns are addressed will have significant impacts on the global community. There is growing attention being placed globally to afforestation efforts, which is highligted by the UN's declaration of the years from 2021 through 2030 as the UN Decade of Ecosystem Resotration [@sewell2020].

>>>>

# Introduction
In 2020, there were 4.1 billion hectares of forestland globally that cover roughly 31.4% of the land [@fao2023]. These forests play an important role in maintaining and growing the land-based carbon sink, currently sequestering about 30% of GHG emmissions [@roe2019]. With increasingly negative climate impacts, the pressure to enhance the terrestrial sink is growing, and one of the tools to achieve this is afforestation. There is growing attention being placed globally to afforestation efforts, which is highligted by the UN's declaration of the years from 2021 through 2030 as the UN Decade of Ecosystem Resotration [@sewell2020], and many of the Nationally Determined Contributions (NDCs) countries have submitted, which detail their plans to keep warming under the 2C threshold, rely to a significant degree on afforestation projects [@roe2019]. This is because of forests proven ability to sequester carbon not only in the stems of trees [@davis2022] but in their soils as well [@guo2021]. At the same time, forests are continually threatened by issues such as rising incomes and food prices and population growth that put pressure on policymakers to allow greater conversion of forestland into farmland. Previous research though has suggested that substantive gains in the carbon sink (+23.8PgCo2e/yr) can be made without sacrificing agricultural land [@griscom2017]. Thus, the manner in which these various and oftentimes competing concerns are addressed will have significant impacts on the global community.
